Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-04 WSSSPE3/report/WSSSPE3_review.tex
Acknowledge SSI and RCUK
adding authors by number&lines of addtions committed to report

\author{tbd by writing and organizing}

%\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Nancy Wilkins-Diehr$^{(3)}$, Neil Chue Hong$^{(4)}$,
%\\Colin C. Venters$^{(5)}$, James Howison$^{(6)}$, Frank Seinstra$^{(7)}$, Matthew Jones$^{(8)}$,
%\\Karen Cranston$^{(9)}$, Thomas L. Clune$^{(10)}$, Miguel de Val-Borro$^{(11)}$, Richard Littauer$^{(12)}$}
%%
%\thanks{{}$^{(1)}$ Computation Institute, 
%University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{dsk@uchicago.edu}}
%%
%\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%%
%\thanks{{}$^{(3)}$ University of California-San Diego, San Diego, CA, USA; \url{wilkinsn@sdsc.edu}}
%%
%\thanks{{}$^{(4)}$ Software Sustainability Institute, 
%University of Edinburgh, Edinburgh, UK; \url{N.ChueHong@software.ac.uk}}
%%
%\thanks{{}$^{(5)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK; \url{C.Venters@hud.ac.uk}}
%%
%\thanks{{}$^{(6)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%%
%\thanks{{}$^{(7)}$ Netherlands eScience Centre, Amsterdam, Netherlands; \url{F.Seinstra@esciencecenter.nl}}
%%
%\thanks{{}$^{(8)}$ National Center for Ecological Analysis and Synthesis, Santa Barbara, CA, USA; \url{jones@nceas.ucsb.edu}}
%%
%\thanks{{}$^{(9)}$ National Evolutionary Synthesis Center, Durham, NC, USA; \url{karen.cranston@nescent.org}}
%%
%\thanks{{}$^{(10)}$ NASA Goddard Space Flight Center, Greenbelt, MD, USA; \url{Thomas.L.Clune@nasa.gov}}
%%
%\thanks{{}$^{(11)}$ Department of Astrophysical Sciences, 
%Princeton University, Princeton, NJ, USA; \url{mdevalbo@astro.princeton.edu}}
%%
%\thanks{{}$^{(12)}$ University of Saarland, Germany; \url{richard.littauer@gmail.com}}
%%

>>>>

\author{Daniel S. Katz$^{(1)}$,
Kyle Niemeyer$^{(2)}$,
Sou-Cheng T. Choi$^{(3)}$,
James Hetherington$^{(4)}$,
Frank L\"{o}ffler$^{(5)}$,
Dan Gunter$^{(6)}$,
Ray Idaszak$^{(7)}$,
Steven R. Brandt$^{(5)}$,
Mark A. Miller$^{(7)}$,
Sandra Gessing$^{(9)}$,
Nick D. Jones$^{(10)}$,
Nic Weber$^{(11)}$,
Gabrielle Allen$^{(12)}$,
Colin C. Venters$^{(13)}$,
Ethan Davis$^{(14)}$,
Lorraine Hwang$^{(15)}$,
Ilian Todorov$^{(16)}$,
Abani Patra$^{(17)}$,
Miguel de Val-Borro$^{(18)}$,
}

%
\thanks{{}$^{(1)}$ Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ institution, city, country; email}
%
\thanks{{}$^{(3)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(4)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(5)}$ Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(7)}$ RENCI, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(9)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(10)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(11)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(12)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA, country; gdallen@illinois.edu}
%
\thanks{{}$^{(13)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; C.Venters@hud.ac.uk}
%
\thanks{{}$^{(14)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(15)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(16)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(17)}$ unit, institution, city, country; email}
%
\thanks{{}$^{(18)}$ Department of Astrophysical Sciences, 
Princeton University, Princeton, NJ, USA; mdevalbo@astro.princeton.edu}
%
